---
title: "Chapter 7"
author: "Alan T. Arnholt"
date: 'Last compiled: `r format(Sys.time(), "%B %d, %Y at %X")`'
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, warning = FALSE, message = FALSE, fig.align = "center")
library(tidyverse)
bki <- read.csv("Burger_King_items.csv")
Cereals <- read.csv("Cereals.csv")
mod_bk <- lm(Fat.g. ~ Protein.g., data = bki)
```

**Objectives:**

I.    Understand the idea behind a **best fit** line

II.   Understand how $r$ helps interpret slope

III.  Know what $R^2$ is

IV.   Know assumptions for linear regression

V.    Know how to create and interpret residual plots

# Step-By-Step Example

## Read in and examine the data

```{r}
nyb <- read.csv("New_York_bridges_2016.csv")
dim(nyb)
tcb <- read.csv("Tompkins_county_bridges_2016.csv")
names(tcb)
TCB <- nyb %>% 
  filter(County == "Tompkins") %>% 
  select(-County, -Manhattan)
```

The problem in the book evaluates 195 bridges from Tompkins county, New York. 

```{r}
ggplot(data = tcb, aes(x = AgeAtInspection, y = Condition)) + 
  geom_point(color = "green4") + 
  theme_bw() + 
  labs(x = "Age At Inspection", title = "Safety score versus age at inspection") + 
  geom_smooth(method = "lm", se = FALSE, color = "black", size = 0.5)
```

```{r}
tcb %>% 
  summarize(xbar = mean(AgeAtInspection), 
            sx = sd(AgeAtInspection),
            ybar = mean(Condition),
            sy = sd(Condition),
            r = cor(AgeAtInspection, Condition),
            b1 = r*sy/sx,
            b0 = ybar - b1*xbar)
# or
mod_tcb <- lm(Condition ~ AgeAtInspection, data = tcb)
summary(mod_tcb)
mod_tcb$coefficients
```


```{r}
# Take 1000 random samples of size 195
set.seed(3)
n <- 1000
b1 <- numeric(n)
for(i in 1:n){
DF <- sample_n(nyb, size = 195, replace = FALSE)
mod <- lm(Condition ~ AgeAtInspection, data = DF)
b1[i] <- mod$coefficients[2]
}
ep <- quantile(b1, probs = c(0.025, 0.975))
ep
```

Note: 95% of the $b_1$ values are between `r round(ep[1],4)` and `r round(ep[2],4)`.

```{r}
data1 = data.frame(b1 = b1) # create data frame to use with ggplot
ggplot(data = data1, aes(x = b1)) + 
  geom_histogram(binwidth = 0.0005, fill = "lightblue", color = "black") + 
  geom_histogram(data = subset(data1, b1 > ep[1] & b1 < ep[2]), binwidth = 0.0005, 
   color = "black", fill = "orange") +
  theme_bw() + 
  geom_vline(xintercept = ep, lty = "dashed") + 
  labs(x = expression(b[1]))
```

## Burger King

Read in the `Burger_King_Items.csv` data set and store the result in `bki`.  Examine the values in `bki`.

```{r}
# Your Code Goes HERE



```

Create a scatter plot of Fat versus Protein.

```{r}
# Your Code Goes HERE




```

Compute the least squares estimates and write the equation of the least squares line.  Store the result of the `lm` object in `mod_bk`.

```{r}
# Your Code Goes HERE






```

The least squares line for regressing Fat onto Protein is:

$$\widehat{\text{Fat}} = xxx + xxx \times \text{Protein}$$

## $R^2$ --- The Variation accounted for by the Model

```{r}
e <- residuals(mod_bk)
fat <- bki$Fat.g. - mean(bki$Fat.g.)
values <- c(e, fat)
type <- rep(c("Residuals", "Fat"), each = 122)
NDF <- data.frame(type = type, values = values)
ggplot(data = NDF, aes(x = type, y = values, fill = type)) + 
  geom_boxplot() + 
  theme_bw() + 
  scale_fill_manual(values = c("green", "purple"))
```

```{r}
1 - var(e)/var(fat)
```

# Step-By-Step Example

Read in the `Cereals.csv` data set and store the data in `Cereals`.  Examine the values in `Cereals`.

```{r}
# Your Code Goes HERE



```

Find the least squares estimates $b_0$ and $b_1$ from regressing `calories` on `sugars`.

```{r}
# Your Code Goes HERE



```

Write the least squares regression equation for regressing `calories` onto `sugars`.

$$\widehat{\text{calories}} = xxx + xxx \times\text{sugars}$$

Create a residuals versus fitted calories plot.

```{r}
mod_cereal <- lm(calories ~ sugars, data = Cereals)
library(broom)
NS <- augment(mod_cereal)
ggplot(data = NS, aes(x = .fitted, y = .resid)) + 
  geom_point(color = "blue") + 
  theme_bw() + 
  labs(x = "Predicted Calories", y = "Residuals") + 
  geom_hline(yintercept = 0, lty = "dashed")
```

# Question # 4 - Homework

```{r}
library(readxl)
chap07ques04 <- read_xlsx("chap07ques04.xlsx")
knitr::kable(chap07ques04)
mod_lm <- lm(`Sales_(in_$1000)` ~ `Number_of_Sales_People_Working`, data = chap07ques04)
summary(mod_lm)
predict(mod_lm, newdata = data.frame(`Number_of_Sales_People_Working` = 18))
```



